---
title: Superbowl Ads
author: The Outliers
output: github_document
---

```{r load-packages, echo = FALSE}
library(tidyverse)
library(fs)
library(dsbox)
library(ggridges)
library(viridis)
library(janitor)
library(scales)
library(gridExtra)
library(emojifont)
library(ggridges)
library(ggrepel)
```


```{r load-data, echo = FALSE}
superbowl_data <- read_csv("data/superbowldata.csv", show_col_types = FALSE)


superbowl_data %>%
  dplyr::distinct(brand)
```


### brand type, ad type and views

```{r, }

q1_p2_data2 <- superbowl_data%>%
  mutate(brand_type = case_when(brand == "Toyota" ~ "Car",
                               brand == "Kia" ~ "Car",
                               brand == "Hynudai" ~ "Car",
                               brand == "Bud Light" ~ "Beverage",
                               brand == "Coca-Cola" ~ "Beverage",
                               brand == "Budweiser" ~ "Beverage",
                               brand == "Pepsi" ~ "Beverage",
                               brand == "Doritos" ~ "Miscellaneous",
                               brand == "E-Trade" ~ "Miscellaneous",
                               brand == "NFL" ~ "Miscellaneous"))
                               

ggplot(q1_p2_data2, aes(x = year, y = brand))+geom_density_ridges(aes(fill = brand_type), scale = 1) + facet_grid(~brand_type)
## brand type, product type count


    ###
```
## Introduction

Every year millions of Americans tune into the most watched  television broadcast in the United States — the Super Bowl. The Super Bowl is the NFL championship game, pitting the winners of the two major conferences, the AFC and the NFC, in a final showdown for all the glory. Due to the game’s high viewership, many brands use the occasion to advertise their products as a means to generate hype and exposure around their brands. In fact, Super Bowl commercials have been regarded as such a cultural phenomenon that many viewers only watch the games to see the beloved commercials. The invaluable exposure the Super Bowl brings to brands also comes with a hefty price as In 2021 alone the cost for a 30-second slot boasted an incredible price tag of $6 million.

Using a FiveThirtyEight dataset of 233 ads from 10 brands that aired the most spots since 2000 we decided to explore the themes that make Super Bowl ads so popular. The dataset includes categorical variables used to classify each ad as `funny`, `show_product_quickly`, `patriotic`, `celebrity`, `danger`, `animals` and/or `use_sex`. while also including variables that that we will use to explore popularity such as `year`, `brand`, `view_count`, `like_count`, `dislike_count`, `favorite_count`, and `comment_count`. We chose to use this dataset because we — like millions other Americans – love Super Bowl ads, and interested in viewing trends over time.

The full data dictionary can be seen below:

## superbowldata.csv

|Variable         |Data         |Description |
|:----------------|:-----------|:--------------------|
|year       | double | Superbowl year|
|brand     | character| Brand for commercial|
|superbowl_ads_dot_com_url    | character | Superbowl ad URL|
|youtube_url             | character | Youtube URL|
|funny              | logical | Contains humor |
|show_product_quickly              | logical | Shows product quickly |
|patriotic             | logical | Patriotic |
|celebrity            |logical| Contains celebrity |
|danger             | logical | Contains danger |
|animals          | logical| Contains animals |
|use_sex            | logical| Uses sexuality |
|id             |character | Youtube ID |
|kind         | character | Youtube Kind |
|etag          | character | Youtube etag |
|view_count           | integer | Youtube view count |
|like_count          | integer| Youtube like count |
|dislike_count          | integer| Youtube dislike count |
|favorite_count         | integer | Youtube favorite count |
|comment_count        |integer | Youtube comment count |
|published_at       | character | Youtube when published |
|title| character  | Youtube title |
|description | character  | Youtube description |
|thumbnail| character | Youtube thumbnail |
|channel_title       | character | Youtube channel name |
|category_id      | character | Youtube content category id |


## Exploring how Super Bowl commercial content trends change over time

### Introduction

We first explore the themes featured in Super Bowl ads and how they have changed over the last 21 years by leveraging the following variables: `funny`, `show_product_quickly`, `patriotic`, `celebrity`, `danger`, `animals`,`use_sex`, and `year`. Each variable (except for year) answers whether or not that specific characteristic was featured in the ad. For example, if an ad contains a celebrity appearance then there is a “yes” inputted for that brands’s commercial. Furthermore, a commercial can feature multiple characteristics such as being funny while using patriotism to raise awareness for said product. We are interested in seeing the changes in commercial advertising over time and predict that patriotic themes have become less prominent over time.

### Approach

[(1-2 paragraphs)
Describe what types of plots you are going to make to address your question.
For each plot, provide a clear explanation as to why this plot (e.g. boxplot, barplot, histogram, etc.) is best for providing the information you are asking about.
The two plots should be of different types, and at least one of the two plots needs to use either color mapping or facets.]

### Analysis

#### Wrangling data

```{r q1_p1_wrangling}

q1_p1_data <- superbowl_data %>%
  group_by(year) %>%
  summarise(funny_count = sum(funny),
            show_product_quickly_count = sum(show_product_quickly),
            patriotic_count = sum(patriotic),
            celebrity_count = sum(celebrity),
            danger_count = sum(danger),
            animals_count = sum(animals),
            use_sex_count = sum(use_sex)) %>%
  pivot_longer(cols = c(funny_count, show_product_quickly_count, patriotic_count, celebrity_count, danger_count, animals_count, use_sex_count), names_to = "type")

```

#### Visualization one

```{r q1_p1_graph}
ggplot(data = q1_p1_data, aes(x = year, y = value, color = type)) +
  geom_line() +
  labs(title = "Prevelance of Different Types of Ads Over Time", x = "Year", y = "Count")
```

```{r q1_p1_graph22}
#g <- ggplot(q1_p1_data, aes(type, value, frame= year, fill  = type)) +
#  geom_col() + labs(title = 'Year: {frame_time}', x = 'Type', y= "Count") + transition_time(year)+ ease_aes('linear') + coord_flip()

#g + transition_states(year, transition_length = 1 , state_length = 4 )

```

#### Visualization two


```{r q1_p2_wrangling}

q1_p2_data <- superbowl_data %>%
  filter(show_product_quickly  == TRUE,
         danger == TRUE,
         celebrity == TRUE)


q1_p2_data %>%
  dplyr::distinct(brand)

```


```{r q1_p2_graph}

ggplot(data = q1_p2_data, aes(x = like_count, y = view_count, color = brand)) +
  geom_point(show.legend = FALSE) +
  labs(title = "Relationship between view and like count for selected content categories",
       x = "Like_Count", y = "View_Count",
       subtitle = "Selected Content: show_product_quickly, danger, celebrity") +
  theme_minimal() +
  scale_y_log10() +
  scale_x_log10() +
  geom_text_repel(aes(label = brand), show.legend = FALSE)

```



[(2-3 code blocks, 2 figures, text/code comments as needed)
In this section, provide the code that generates your plots. Use scale functions to provide nice axis labels and guides.
You are welcome to use theme functions to customize the appearance of your plot, but you are not required to do so.
All plots must be made with ggplot2. Do not use base R or lattice plotting functions.]

### Discussion

[(1-3 paragraphs)
In the Discussion section, interpret the results of your analysis. Identify any trends revealed (or not revealed) by the plots.
Speculate about why the data looks the way it does.]

## Exploring the most popular Super Bowl commercial brands

### Introduction

[Hebron's work here]

### Approach

Graph 1:
Originally, for our first graph, we planned to use a 100% stacked bar chart to compare the proportion of likes out of total reactions received by each brand for all commercials in the dataset. When we tried this, however, the visualization looked very crowded and did not look appealing when we changed the width of the bars. We instead decided that a lollipop plot of the same data was easier to interpret and more aesthetically appealing. In order to display the brands in a neat manner, we put them on the y-axis and the proportions on the x. The lollipop plot is effective in this case, as it clearly demonstrates which brands received a higher relative number of likes. This metric is important, as it gauges how audiences react to a video, giving us some idea of how well each of the brands is received by their respective audiences. In addition, this plot has a fairly reasonable data-to-ink ratio and the use of lines, as opposed to bars, creates a less crowded appearance.

Graph 2:
For our second graph, we created a scatterplot using `geom_point`. While we personally believe that looking at the proportion of likes relative to total interactions is the best way to gauge the audience's opinion on each brand's commercials, we thought it would also be important to look at other measures of popularity, in this case, `avg_total_views` and `avg_total_comments`. These were both variables we generated by calculating the average total views and comments each brand received per commercial. We put `avg_total_views` on the x-axis and `avg_total_comments` on the y-axis, coloring by brand. Due to the large discrepancy in values of view and comment count, we decided to change the scales of the x-axis and y-axis to a Log10 scale. This made it much easier to intrepret the graph and spaced out the points in a way that made them easy to see. We believe this visualization is appropriate for our analysis, as it clearly demonstrates the which brands receive the most amount of views and comments per commercial. This graph is a nice compliment to our first visualization and will be helpful to see how each brand is represented in each scenario.


### Analysis

```{r q2_p1_wrangling}

q2_p1_data <- filter(superbowl_data, like_count != is.na(like_count) & dislike_count != is.na(dislike_count)) %>%
  group_by(brand) %>%
  mutate(likes_total = sum(like_count),
         dislikes_total = sum(dislike_count),
         proportion_likes_total = likes_total / (dislikes_total + likes_total))

```

```{r q2_p1_graph, echo=FALSE}

ggplot(q2_p1_data, aes(x = proportion_likes_total, y = brand)) +
    geom_segment(aes(y = reorder(brand, proportion_likes_total), yend = reorder(brand, proportion_likes_total), x = 0, xend = proportion_likes_total), color = "dodgerblue1", size = 2) +
  geom_point(color = "dodgerblue1", size = 3) +
  coord_cartesian(xlim = c(.75, 1)) +
  labs(title = "Proportion of likes received out of total video interactions, by brand", x = "Proportion of likes out of total interactions",
       y = "Brand", subtitle = "(Video interactions = likes + dislikes)") +
    theme(panel.background = element_blank(), axis.ticks.y = element_blank(),
          axis.text.y = element_text(size = 11, color = "black"),
          axis.text.x = element_text(size = 11, color = "black"),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12))
```

```{r Q2_p2_wrangling, }

q2_p2_data <- filter(superbowl_data, comment_count != is.na(comment_count) &
                         view_count != is.na(view_count)) %>%
  group_by(brand) %>%
  summarise(avg_total_comments = mean(comment_count),
         avg_total_views = mean(view_count))

```

```{r q2_p2_graph}

ggplot(q2_p2_data, aes(x = avg_total_views, y = avg_total_comments)) +
         geom_point(aes(color = brand), show.legend = FALSE) +
  geom_text_repel(aes(label = brand)) +
  scale_y_log10() +
  scale_x_log10(labels = unit_format(unit = "M", scale = 1e-6)) +
  labs(x = "Average Total Views", y = "Average Total Comments",
       title = "Average Total Comments vs. Average Total Views, by brand",
       caption = "Axes on log10 scale, labels are raw units")

```