---
title: Superbowl Ads 
author: The Outliers
output: github_document
---

```{r load-packages, echo = FALSE}
library(tidyverse)
library(fs)
library(dsbox)
library(ggridges)
library(viridis)
library(janitor)
library(scales)
library(gridExtra)
library(emojifont)
library(ggridges)
library(ggrepel)
```

```{r load-data, echo = FALSE}
superbowl_data <- read_csv("data/superbowldata.csv", show_col_types = FALSE)
```

## Introduction

Every year millions of Americans tune into the most watched  television broadcast in the United States — the Super Bowl. The Super Bowl is the NFL championship game, pitting the winners of the two major conferences, the AFC and the NFC, in a final showdown for all the glory. Due to the game’s high viewership, many brands use the occasion to advertise their products as a means to generate hype and exposure around their brands. In fact, Super Bowl commercials have been regarded as such a cultural phenomenon that many viewers only watch the games to see the beloved commercials. The invaluable exposure the Super Bowl brings to brands also comes with a hefty price as In 2021 alone the cost for a 30-second slot boasted an incredible price tag of $6 million.

Using a FiveThirtyEight dataset of 233 ads from 10 brands that aired the most spots since 2000 we decided to explore the themes that make Super Bowl ads so popular. The dataset includes categorical variables used to classify each ad as `funny`, `show_product_quickly`, `patriotic`, `celebrity`, `danger`, `animals` and/or `use_sex`. while also including variables that that we will use to explore popularity such as `year`, `brand`, `view_count`, `like_count`, `dislike_count`, `favorite_count`, and `comment_count`. We chose to use this dataset because we — like millions other Americans – love Super Bowl ads, and interested in viewing trends over time.

## Exploring how Super Bowl commercial content trends change over time 

### Introduction

We first explore the themes featured in Super Bowl ads and how they have changed over the last 21 years by leveraging the following variables: `funny`, `show_product_quickly`, `patriotic`, `celebrity`, `danger`, `animals`,`use_sex`, and `year`. Each variable (except for year) answers whether or not that specific characteristic was featured in the ad. For example, if an ad contains a celebrity appearance then there is a “yes” inputted for that brands’s commercial. Furthermore, a commercial can feature multiple characteristics such as being funny while using patriotism to raise awareness for said product. We are interested in seeing the changes in commercial advertising over time and predict that patriotic themes have become less prominent over time.

### Approach

[(1-2 paragraphs)
Describe what types of plots you are going to make to address your question.
For each plot, provide a clear explanation as to why this plot (e.g. boxplot, barplot, histogram, etc.) is best for providing the information you are asking about. 
The two plots should be of different types, and at least one of the two plots needs to use either color mapping or facets.]

### Analysis

#### Wrangling data

```{r q1_p1_wrangling}

q1_p1_data <- superbowl_data %>%
  group_by(year) %>%
  summarise(funny_count = sum(funny),
            show_product_quickly_count = sum(show_product_quickly),
            patriotic_count = sum(patriotic),
            celebrity_count = sum(celebrity),
            danger_count = sum(danger),
            animals_count = sum(animals),
            use_sex_count = sum(use_sex)) %>%
  pivot_longer(cols = c(funny_count, show_product_quickly_count, patriotic_count, celebrity_count, danger_count, animals_count, use_sex_count), names_to = "type")

```

#### Visualization one 

```{r q1_p1_graph}
ggplot(data = q1_p1_data, aes(x = year, y = value, color = type)) +
  geom_line() +
  labs(title = "Prevelance of Different Types of Ads Over Time", x = "Year", y = "Count")
```

#### Visualization two 


```{r q1_p2_wrangling}

q1_p2_data <- superbowl_data %>%
  filter(show_product_quickly  == TRUE, 
         danger == TRUE, 
         celebrity == TRUE)

```


```{r q1_p2_graph}

ggplot(data = q1_p2_data, aes(x = like_count, y = view_count, color = brand)) +
  geom_point(show.legend = FALSE) + 
  labs(title = "Relationship between view and like count for selected content categories",
       x = "Like_Count", y = "View_Count",
       subtitle = "Selected Content: show_product_quickly, danger, celebrity") + 
  theme_minimal() +
  scale_y_log10() +
  scale_x_log10() +
  geom_text_repel(aes(label = brand), show.legend = FALSE) 

```

[(2-3 code blocks, 2 figures, text/code comments as needed)
In this section, provide the code that generates your plots. Use scale functions to provide nice axis labels and guides.
You are welcome to use theme functions to customize the appearance of your plot, but you are not required to do so.
All plots must be made with ggplot2. Do not use base R or lattice plotting functions.]

### Discussion

[(1-3 paragraphs)
In the Discussion section, interpret the results of your analysis. Identify any trends revealed (or not revealed) by the plots.
Speculate about why the data looks the way it does.]

## Exploring the most popular Super Bowl commercial brands

### Introduction

[Hebron's work here]

### Approach

[(1-2 paragraphs)
Describe what types of plots you are going to make to address your question.
For each plot, provide a clear explanation as to why this plot (e.g. boxplot, barplot, histogram, etc.) is best for providing the information you are asking about. 
The two plots should be of different types, and at least one of the two plots needs to use either color mapping or facets.]

### Analysis

```{r q2_p1_wrangling}

q2_p1_data <- filter(superbowl_data, like_count != is.na(like_count) & dislike_count != is.na(dislike_count)) %>%
  group_by(brand) %>%
  mutate(likes_total = sum(like_count),
         dislikes_total = sum(dislike_count),
         proportion_likes_total = likes_total / (dislikes_total + likes_total))

```

```{r q2_p1_graph, echo=FALSE}

ggplot(q2_p1_data, aes(x = proportion_likes_total, y = brand)) + 
    geom_segment(aes(y = reorder(brand, proportion_likes_total), yend = reorder(brand, proportion_likes_total), x = 0, xend = proportion_likes_total), color = "dodgerblue1", size = 2) + 
  geom_point(color = "dodgerblue1", size = 3) + 
  coord_cartesian(xlim = c(.75, 1)) + 
  labs(title = "Proportion of likes received out of total video interactions (likes + dislikes)", x = "Proportion of likes out of total interactions", 
       y = "Brand") + 
    theme(panel.background = element_blank(), axis.ticks.y = element_blank(),
          axis.text.y = element_text(size = 11, color = "black"), 
          axis.text.x = element_text(size = 11, color = "black"),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12))
```

```{r Q2_p2_wrangling}

q2_p2_data <- superbowl_data %>%
  filter(brand == c("Kia", "Pepsi", "E-Trade"))%>%
  group_by(year, brand) %>%
  mutate(proportion_likes_yearly = like_count / (like_count + dislike_count))

```

```{r q2_p2_graph}

ggplot(data = q2_p2_data, aes(x = year, y = proportion_likes_yearly, group = brand))  +
  geom_line() + 
  labs(title = "Proportion of Likes/Dislikes over time for the top 3 Brands", x = "Year", y = "Count") + theme_minimal()

```

[(2-3 code blocks, 2 figures, text/code comments as needed)
In this section, provide the code that generates your plots. Use scale functions to provide nice axis labels and guides.
You are welcome to use theme functions to customize the appearance of your plot, but you are not required to do so.
All plots must be made with ggplot2. Do not use base R or lattice plotting functions.]

### Discussion

(1-3 paragraphs)
In the Discussion section, interpret the results of your analysis. Identify any trends revealed (or not revealed) by the plots.
Speculate about why the data looks the way it does.

## Presentation

Our presentation can be found [here](presentation/presentation.html).

## Data 

Include a citation for your data here. 
See http://libraryguides.vu.edu.au/c.php?g=386501&p=4347840 for guidance on proper citation for datasets. 
If you got your data off the web, make sure to note the retrieval date.

## References

List any references here. You should, at a minimum, list your data source.
