---
title: "Project proposal"
author: "The Outliers"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(dplyr)
```

## Dataset

```{r read-data}
youtube <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-02/youtube.csv')
summary(youtube)
head(youtube)
names(youtube)
```
We chose to use the Superbowl Ad dataset. The dataset came from FiveThirtyEight, but it was originally sourced from superbowl-ads.com.  The dataset has 247 rows and 25 columns. The variable names include year, brand, superbowl_ads_dot_com_url, youtube_url, funny, show_product_quickly, patriotic, celebrity, danger, animals, use_sex, id, kind, etag, view_count, like_count, dislike_count, favorite_count, comment_count, published_at, title, description, thumbnail, channel_title, and category_id. We chose to use this dataset because we all love Superbowl ads, and we were initially interested in viewing trends over time. This dataset has a variable dedicated to the ad’s published date and several variables surrounding viewer preferences. 

## Questions

The two questions you want to answer.

#### Question 1 

Question 1: 

How do content trends change over time? We will leverage the following variables to answer this question: 

```{r Q1-variables}

Q1data <- youtube %>% 
  select(funny, show_product_quickly, patriotic, celebrity, danger, animals, use_sex, year)

glimpse(Q1data)

```

#### Question 


## Analysis plan

A plan for answering each of the questions including the variables involved, variables to be created (if any), external data to be merged in (if any).
