---
title: "Project proposal"
author: "The Outliers"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(dplyr)
```

## Dataset

```{r read-data}
youtube <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-02/youtube.csv')
summary(youtube)
head(youtube)
names(youtube)
```
We chose to use the Superbowl Ad dataset. The dataset came from FiveThirtyEight, but it was originally sourced from superbowl-ads.com.  The dataset has 247 rows and 25 columns. The variable names include year, brand, superbowl_ads_dot_com_url, youtube_url, funny, show_product_quickly, patriotic, celebrity, danger, animals, use_sex, id, kind, etag, view_count, like_count, dislike_count, favorite_count, comment_count, published_at, title, description, thumbnail, channel_title, and category_id. We chose to use this dataset because we all love Superbowl ads, and we were initially interested in viewing trends over time. This dataset has a variable dedicated to the ad’s published date and several variables surrounding viewer preferences. 

## Questions

The two questions you want to answer.

#### Question 1 

Question 1: 

We would like to explore how content trends change over time. We will leverage the following variables to answer this question funny, show_product_quickly, patriotic, celebrity, danger, animals, use_sex, like_count year. Specifically we will explore the distribution of certain commercial content categories (funny, show_product_quickly patriotic, celebrity, danger, animlas, use_sex) over time. We are interested in seeing the changes in commercial advertising over time. We predict that patriotic themes in commericals would decrease
over time. 



```{r Q1-variables}

Q1data <- youtube %>% 
  select(funny, show_product_quickly, patriotic, celebrity, danger, animals, use_sex, like_count, year)

glimpse(Q1data)

```

We chose not to use published_date for our time series analyses because some of the videos were uploaded
years later than they initially ran on live television.

#### Question 2

For our second question, we would like to explore which brands are most popular amongst viewers on Youtube. Specifically, for each brand represented in the data, we plan to look at what proportion of the reactions (likes + dislikes) each brand receives on their Super Bowl commercials. We plan to look at the proportion of likes and dislikes, on average, over the history of the dataset. We may also explore how the proportion of likes and dislikes changes over time, as some brands may have increased / decreased in popularity over time. 

```{r Q2-variables}

Q2data <- youtube %>%
  select(brand, like_count, dislike_count, year)

glimpse(Q2data)

```

We chose not to use published_date for our time series analyses because some of the videos were uploaded
years later than they initially ran on live television.

## Analysis plan



A plan for answering each of the questions including the variables involved, variables to be created (if any), external data to be merged in (if any).


Both of our questions use the variables in the original dataset: Superbowl Ads. Therefore, we do not need to merge any external data.


