---
title: "Project proposal"
author: "The Outliers"
output: github_document
---

## Load Packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse)
library(dplyr)
```

## Dataset

```{r read-data, warning=FALSE, show_col_types = FALSE}
youtube <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-02/youtube.csv")
summary(youtube)
glimpse(youtube)
names(youtube)
```
We chose to use the Superbowl Ad dataset which contains a list of ads from the 10 brands 
that had the most advertisements in Super Bowls from 2000 to 2020. The dataset came from FiveThirtyEight, but it was originally sourced from superbowl-ads.com.  The dataset has 247 rows and 25 columns. Each row represents an Superbowl ad aired 
between 2000 to 2020 with 25 characteristics. We chose to use this dataset because we all love Superbowl ads, and we were initially interested in viewing trends over time. This dataset has a variable dedicated to the ad’s published date and several variables surrounding viewer preferences. 

## Questions


#### Question 1 

We would like to explore how content trends change over time. We will leverage the following variables to answer this question: `funny`, `show_product_quickly`, `patriotic`, `celebrity`, `danger`, `animals`, `use_sex`, `like_count year`. By examining the prevalence of these characteristics over time, we should be able to see how companies have changed their approach to advertising. It is difficult to say how all of these different content types have changed over time, but we do believe that use patriotic marketing has likely decreased recently. We look forward to exploring whether this hypothesis is correct and seeing how the patterns of the variables have changed as well.


```{r Q1-variables, warning=FALSE}

Q1data <- youtube %>%
  select(funny, show_product_quickly, patriotic, celebrity, danger, animals, use_sex, like_count, year)

glimpse(Q1data)
```

We chose not to use published_date for our time series analyses because some of the videos were uploaded
years later than they initially ran on live television.

#### Question 2

For our second question, we would like to explore which brands are most popular among viewers on Youtube. Specifically, for each brand represented in the data, we plan to look at what proportion of the reactions (likes + dislikes) each brand receives on their Super Bowl commercials. We plan to look at the proportion of likes, on average, over the history of the dataset. We may also explore how the proportion of likes changes over time, as some brands may have increased / decreased in popularity over time. 

We would like to explore this question because we are interested in discovering which brands are received best by those who watch Super Bowl commercials. That way, next time we all watch the Super Bowl, we know which ads are likely to be best. This analysis should also provide some insight into which brands are more popular generally, which should be interesting to see as well. 



```{r Q2-variables, warning=FALSE}

Q2data <- youtube %>%
  select(brand, like_count, dislike_count, year)

glimpse(Q2data)
```

We chose not to use `published_date` for our time series analyses because some of the videos were uploaded
years later than they initially ran on live television.

## Analysis plan

To address Question 1, we plan on creating two plots: 
    
  To address Question 1, we will first have to create a new variable that counts the occurrence of different content types for each year in the dataset. There are 7 different content types (`funny`, `show_product_quickly`, `patriotic`, `celebrity`, `danger`, `animals`, or `use_sex`) and so we will generate 7 new variables (`funny_count`, `show_product_quickly_count`, `patriotic_count`, `celebrity_count`, `danger_count`, `animals_count`, `use_sex_count`) that count the occurrence of each of these content tags. For example, if there are 7 commercials in 2000 that are tagged as `funny`, the new variable `funny_count` will equal 7 for that year. Videos that do not have content tags will be completely omitted from the analysis. This plot is best for our question because it will clearly show how the use of different content types has changed over time. 
  The second plot will be a deep dive into one content area. After creating the first plot and conducting a simple analysis, we will choose a content area that has an interesting trend (prevalence has increased / decreased significantly, prevalence fluctuates significantly, etc.). For all the videos that contain the category we choose, we will use `geom_point` to look at the relationship between `like_count` (x-axis) and `view_count` (y-axis). In addition, we will color the observations by `brand` to see if there is any interaction there with respect to this relationship. This way we can identify any brands that have unique relationships between `like_counts` and `view_counts` in the content area of our choosing, which may help explain whatever pattern we originally identify. 
 

To address Question 2, we plan on creating two plots:

  For the first step of our analysis, we will look at the proportion of likes each brand receives in a new variable called `proportion_likes_total`. To calculate this variable, we first need to sum the total number of likes and dislikes each brand receives across all of its advertisements in the dataset. We will then calculate `proportion_likes_total` for each brand based on the cumulative proportion of likes to total reactions (likes + dislikes). To visualize this information, each of the 10 brand’s proportion of likes will be represented in a stacked bar chart. We will determine the appropriate axis orientation for this information once we have started our analysis. 
  
  Our second plot will explore like/dislike trends by brand over time. We are going to pick the top three brands based on our previous analysis (highest proportion of likes). To see how brand popularity has changed over time, we will need to create a new variable for the brands we select: `proportion_likes_yearly`. Unlike the variable used in the first visualization, this variable will look at the proportion of likes each brand receives for each year they are represented in the dataset. In this case, `proportion_likes_yearly` will be on the y-axis, and `year` will be on the x-axis. This graph will show us trends in the proportion of likes for the three most popular brands. One issue we may run into is that every brand we select may not have a commercial from each year. We may have to carefully select the time period we represent in our analysis so that each brand has an observation for every year we plot.


  Both of our questions use the variables in the original dataset: Superbowl Ads. Therefore, we do not need to merge any external data.
