---
title: "Project proposal"
author: "The Outliers"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(dplyr)
```

## Dataset

```{r read-data}
youtube <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-02/youtube.csv')
summary(youtube)
head(youtube)
names(youtube)
```
We chose to use the Superbowl Ad dataset. The dataset came from FiveThirtyEight, but it was originally sourced from superbowl-ads.com.  The dataset has 247 rows and 25 columns. The variable names include year, brand, superbowl_ads_dot_com_url, youtube_url, funny, show_product_quickly, patriotic, celebrity, danger, animals, use_sex, id, kind, etag, view_count, like_count, dislike_count, favorite_count, comment_count, published_at, title, description, thumbnail, channel_title, and category_id. We chose to use this dataset because we all love Superbowl ads, and we were initially interested in viewing trends over time. This dataset has a variable dedicated to the ad’s published date and several variables surrounding viewer preferences. 

## Questions


#### Question 1 

We would like to explore how content trends change over time. We will leverage the following variables to answer this question: `funny`, `show_product_quickly`, `patriotic`, `celebrity`, `danger`, `animals`, `use_sex`, `like_count year`. By examining the prevalence of these characteristics over time, we should be able to see how companies have changed their approach to advertising. It is difficult to say how all of these different content types have changed over time, but we do believe that use patriotic marketing has likely decreased recently. We look forward ot exploring whether this hypothesis is correct and seeing how the patterns of the variables have changed as well.


```{r Q1-variables}

Q1data <- youtube %>% 
  select(funny, show_product_quickly, patriotic, celebrity, danger, animals, use_sex, like_count, year)

glimpse(Q1data)

```

We chose not to use published_date for our time series analyses because some of the videos were uploaded
years later than they initially ran on live television.

#### Question 2

For our second question, we would like to explore which brands are most popular amongst viewers on Youtube. Specifically, for each brand represented in the data, we plan to look at what proportion of the reactions (likes + dislikes) each brand receives on their Super Bowl commercials. We plan to look at the proportion of likes and dislikes, on average, over the history of the dataset. We may also explore how the proportion of likes and dislikes changes over time, as some brands may have increased / decreased in popularity over time. 

We would like to explore this question because we are interested in discovering which brands are received best by those who watch Super Bowl commercials. That way, next time we all watch the Super Bowl, we know which ads are likely to be best. This analysis should also provide some insight into which brands are more popular generally, which should be interesting to see as well. 



```{r Q2-variables}

Q2data <- youtube %>%
  select(brand, like_count, dislike_count, year)

glimpse(Q2data)

```

We chose not to use `published_date` for our time series analyses because some of the videos were uploaded
years later than they initially ran on live television.

## Analysis plan

To address Question 1, we plan on creating two plots: 
    
  The first plot will be a geom_line plot with year on the x-axis and like_count on the y-axis. We will color the lines by type of video, after creating a variable type that encompasses whether the video is categorized as “funny,” “show_product_quickly,” “patriotic,” “celebrity,” “danger,” “animals,” or “use_sex.” This plot is best for our question because it will clearly show trends over time faceted by category, which is exactly what we are trying to analyze. 
  
  The second plot will be a deep dive into one content area. After creating the first plot and conducting a simple analysis, we will choose a content area that has an interesting trend (e.g., very high likes in some years, very low likes in others). We will dive into this category and analyze `like_count`, `view_count`, and `dislike_count` over the years with a faceted barplot. 

To address Question 2, we plan on creating two plots:

  For the first step of our analysis, we will look at the average proportion of likes and dislikes for each brand across all the time periods. In other words, we will look at each brand's proportion of likes and dislikes for every year they are represented, and then average these proportions across time. While this will weight each year equally, in order to properly represent brands that have not run commercials every year, we felt this approach was the most appropriate. To view this visually, we will first create a new variable called `proportion_likes`, which divides the number of likes (`like_count`) by total reactions (`like_count` + `dislike_count`) for every year. We will then take the average of this proportion for each brand across all time periods to create a new variable: `average_proportion`. The graph we plan to use to represent this will be a 100% stacked bar chart. This should show which brands are most well received on average. 
  #need to fix some stuff here. 

  Our second plot will explore like/dislike trends over time. We are going to pick the top three brands based on our previous analysis (highest proportion of likes). We will use geom_line and color the lines by brand.  The `proportion_likes` variable that we created for the previous analysis will be on the y-axis, and `published_date` will be on the x-axis. This graph will show us trends in the proportion of likes for the three most popular brands.

  Both of our questions use the variables in the original dataset: Superbowl Ads. Therefore, we do not need to merge any external data.


