---
title: "Graphs for el prez"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

## Plots

```{r}
youtube <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-02/youtube.csv")
glimpse(youtube)
```

### Question 1 hi

To address Question 1, we will first have to create a new variable that counts the occurrence of different content types for each year in the dataset. There are 7 different content types (funny, show_product_quickly, patriotic, celebrity, danger, animals, or use_sex) and so we will generate 7 new variables (funny_count, show_product_quickly_count, patriotic_count, celebrity_count, danger_count, animals_count, use_sex_count) that count the occurrence of each of these content tags. For example, if there are 7 commercials in 2000 that are tagged as funny, the new variable funny_count will equal 7 for that year. Videos that do not have content tags will be completely omitted from the analysis. 


```{r wrangling_q1}
youtube <- youtube %>%
  group_by(year) %>%
  summarise(funny_count = sum(funny),
            show_product_quickly_count = sum(show_product_quickly),
            patriotic_count = sum(patriotic),
            celebrity_count = sum(celebrity),
            danger_count = sum(danger),
            animals_count = sum(animals),
            use_sex_count = sum(use_sex)) %>%
  pivot_longer(cols = c(funny_count, show_product_quickly_count, patriotic_count, celebrity_count, danger_count, animals_count, use_sex_count), names_to = "type")

youtube
```

line graph of content type prevalency over time

```{r q1_graph_1}
ggplot(data = youtube, aes(x = year, y = value, color = type)) +
  geom_line() +
  labs(title = "Prevelance of Different Types of Ads Over Time", x = "Year", y = "Count")
```


The second plot will be a deep dive into one content area. After creating the first plot and conducting a simple analysis, we will choose a content area that has an interesting trend (prevalence has increased / decreased significantly, prevalence fluctuates significantly, etc.). For all the videos that contain the category we choose, we will use geom_point to look at the relationship between like_count (x-axis) and view_count (y-axis). In addition, we will color the observations by brand to see if there is any interaction there with respect to this relationship. This way we can identify any brands that have unique relationships between like_counts and view_counts in the content area of our choosing, which may help explain whatever pattern we originally identify.


Based on our first plot, we found that danger_count, show_product_quickly_count, and 
celebrity count had interesting trends. We will do a deep dive into these 
categories to explore the relationship between like_count and view count. 

```{r q1_graph_2}

ya_youtube <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-02/youtube.csv")

ya_youtube %>%
  filter(show_product_quickly  == TRUE, 
         danger == TRUE, 
         celebrity == TRUE)


ggplot(data = ya_youtube, aes(x = like_count, y = view_count, color = brand)) +
  geom_point() + 
  labs(title = "Proportion of Likes/Dislikes Over time for ads containing danger,
       celebrities, and shows_product_quickly", x = "Like_Count", y = "View_Count") + theme_minimal()




```



### Question 2





```{r wranging_q2}

```

For the first step of our analysis, we will look at the proportion of
likes each brand receives in a new variable called
`proportion_likes_total`. To calculate this variable, we first need to
sum the total number of likes and dislikes each brand receives across
all of its advertisements in the dataset. We will then calculate
`proportion_likes_total` for each brand based on the cumulative
proportion of likes to total reactions (likes + dislikes). To visualize
this information, each of the 10 brand’s proportion of likes will be
represented in a stacked bar chart. We will determine the appropriate
axis orientation for this information once we have started our analysis.

```{r q2_graph_1 }

```


Based on our findings in the previous analysis the top 3 brands are kia, nfl, 
and pesi. 

Our second plot will explore like/dislike trends by brand over time. We
are going to pick the top three brands based on our previous analysis
(highest proportion of likes). To see how brand popularity has changed
over time, we will need to create a new variable for the brands we
select: `proportion_likes_yearly`. Unlike the variable used in the first
visualization, this variable will look at the proportion of likes each
brand receives for each year they are represented in the dataset. In
this case, `proportion_likes_yearly` will be on the y-axis, and `year`
will be on the x-axis. This graph will show us trends in the proportion
of likes for the three most popular brands. One issue we may run into is
that every brand we select may not have a commercial from each year. We
may have to carefully select the time period we represent in our
analysis so that each brand has an observation for every year we plot.

Both of our questions use the variables in the original dataset:
Superbowl Ads. Therefore, we do not need to merge any external data.

```{r Q2_graph_2_data_wrangling}

youtube2 <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-02/youtube.csv")

youtube2 <- youtube2 %>%
  filter(brand == c("Kia", "NFL", "Pepsi"))%>%
  group_by(year, brand) %>%
  summarise(total_dislikes = sum(dislike_count), 
            total_likes = sum(like_count))
                                 

youtube2 <- youtube2 %>%
  mutate(proportion_likes_yearly = total_likes / (total_likes + total_dislikes))

youtube2 
```
```{r q2_graph_2}
ggplot(data = youtube2, aes(x = year, y = proportion_likes_yearly, color = brand)) +
  geom_point() + 
  labs(title = "Proportion of Likes/Dislikes over time for the top 3 Brands", x = "Year", y = "Count") + theme_minimal()
```

