---
title: "The Battle of the Superbowl Ads"
subtitle: "Who will persevere?"
author: "The Outliers <br> Davis Jones, Kate Straneva, Hebron Daniel, Sophie Dalldorf"
institute: "Duke University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
# Remove any packages from this list that you're not using
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringan)
library(xaringanthemer)
library(tidyverse)
library(dplyr)
library(ggplot2)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(
  fig.retina = 3, 
  dpi = 300, 
  fig.width = 6, 
  fig.asp = 0.618, 
  out.width = "70%"
  )
```

```{r load-data, include=FALSE}
youtube <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-02/youtube.csv")
```

```{r style-slides, echo = FALSE}


style_duo(primary_color = "#1F4257", secondary_color = "#F97B64",
          title_slide_background_image = "desktop/superbowl.jpeg")



```


# Introduction: Superbowl Ads

.pull-left[
About This Data:

- Came from FiveThirtyEight

- 247 rows and 25 columns

- Tells us information about brands, types of videos (funny, patriotic, etc.), years released, likes/dislikes, and more.
]

--

.pull-right[
Why This Dataset? 

- We all love Superbowl ads!

- We were interested to see trends over time and explore which brands were most popular!
]
---

#Question 1...

- Our first question aims to examine how content trends have changed over time.


---

## First Plot

We first show the number of videos in each category over time:

```{r data-wrangling, echo = FALSE}
youtube <- youtube %>%
  group_by(year) %>%
  summarise(funny_count = sum(funny),
            show_product_quickly_count = sum(show_product_quickly),
            patriotic_count = sum(patriotic),
            celebrity_count = sum(celebrity),
            danger_count = sum(danger),
            animals_count = sum(animals),
            use_sex_count = sum(use_sex)) %>%
  pivot_longer(cols = c(funny_count, show_product_quickly_count, patriotic_count, celebrity_count, danger_count, animals_count, use_sex_count), names_to = "type")
```

.pull-left[
this will be our graph
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
ggplot(data = youtube, aes(x = year, y = value, color = type)) +
  geom_line() +
  labs(title = "Prevelance of Different Types of Ads Over Time", x = "Year", y = "Count") +
  scale_xaringan_fill_discrete()
```

]

.pull-right[
this will be our description

]


---

## Second Plot

Second, we wanted to conduct a deep dive into one content area's trends, so we created a geom_point graph that shows unique like_counts and view_counts colored by brand.

.pull-left[
this will be our graph
```{r}
scale_xaringan_fill_discrete()
```

]

.pull-right[
this will be our description

]

.footnote[
any footnotes??

]

---

# Question 2...

For our second analysis, we chose to explore which brands are most popular among viewers on Youtube using likes and dislikes.

---

## First Plot

This first graph shows the proportion of likes and dislikes for each brand:

.pull-left[
this will be our graph
```{r}
scale_xaringan_fill_discrete()
```

]

.pull-right[
this will be our description

]

.footnote[
any footnotes??

]

---

## Second Plot

The second plot shows like/dislike trends by brand over time. We picked the top three brands based on the highest proportion of likes and presented them below:

.pull-left[
this will be our graph
```{r}
scale_xaringan_fill_discrete()
```
]

.pull-right[
this will be our description

]

.footnote[
any footnotes??

]

---

# Questions?

---
